A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-22 tex-arxiv/article.tex
start writing about model choice

One important characteristic of the MDP is that it is history-agnostic -- the future state distribution of the system is uniquely defined by its current state. While technically true for physical environments, it is often the case that instead of a complete state representation vector $\mathbf{s}$ we are instead operating on a more limited \emph{observation} $\mathbf{o}$ (often interchangeably referred to as $\mathbf{s}$ for brevity), where each element $o_i$ is given by some function $f_i(\mathbf{s})$. It is therefore possible that historical observations contain information about hidden system state variables even assuming the MDP formalism holds for the underlying environment. An example of this can be the case when individual observations contain only the current position of an object but not its derivatives \citep{zhang2018deep}. In such cases it may prove beneficial to break with the formalism further, by redefining the policy to operate on sequences of $k+1$ previous states/observations

@@

These adjustments allow for the employment of sequence-to-sequence predictor architectures also studied in other areas of machine learning such as recurrent neural networks (RNNs) \citep{rumelhart1985learning} and transformers \citep{vaswani2017attention}. Finally, if continuous action spaces are permitted it is no great stretch to also consider cases where the action corresponds to a predicted future state that may be used for static motion planning or in a dynamic error-based controller

@@

Simulation allows recording exact pose information directly at regular time intervals, but setting up the scene necessitates creating a virtual environment where the task can be performed. In addition, for realistic interactions a physics simulation and immersive interface such as VR is required, but even this does not present the human demonstrator with the haptic feedback of actually performing the task in the real world. As such we decided that the benefits of simple setup and inherently natural interaction with the physical scene outweigh the precision and cost advantages of simulated environments, and selected motion capture as the source of demonstration data.

The outputs of the \emph{Optitrack} motion capture system are timestamped messages containing pose data for each pre-defined rigid body in a Cartesian coordinate system.

>>>>

One important characteristic of the MDP is that it is history-agnostic -- the future state distribution of the system is uniquely defined by its current state. While technically true for physical environments, it is often the case that instead of a complete state representation vector $\mathbf{s}$ we are instead operating on a more limited \emph{observation} $\mathbf{o}$ (often interchangeably referred to as $\mathbf{s}$ for brevity), where each element $o_i$ is given by some function $f_i(\mathbf{s})$. It is therefore possible that historical observations contain information about hidden system state variables even assuming the MDP formalism holds for the underlying environment. An example of this can be the case when individual observations contain only the current position of an object but not its derivatives, as in video data. In such situations it may prove beneficial to break with the formalism further, by redefining the policy to operate on sequences of $k+1$ previous states/observations

@@

These adjustments allow for the employment of sequence-to-sequence predictor architectures also studied in other areas of machine learning such as recurrent neural networks (RNNs) \citep{rumelhart1985learning} and transformers \citep{vaswani2017attention}. Finally, if continuous action spaces are permitted it is no great stretch to also consider formats where the action corresponds to a predicted future state to be used for static motion planning or in a feedback controller

@@

Simulation allows recording exact pose information directly at regular time intervals, but setting up the scene necessitates creating a virtual environment where the task can be performed. In addition, for realistic interactions a physics simulation and immersive interface such as VR is required, but even this does not present the human demonstrator with the haptic feedback of actually performing the task in the real world. As such we decided that the benefits of simple setup and inherently natural interaction with the physical scene outweigh the precision and cost advantages of simulated environments, and selected motion capture as the source of demonstration data. For extracting additional information specific to the throwing task, we also track the object thrown and use its pose information to annotate each observation with target coordinates extrapolated from its flight arc and a release timing signal determined by heuristics described below.

The next crucial decision to make is
